% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
\textbf{\Large FRANCIS MARFO}\\[2pt] % Name
Lincoln, Nebraska | \href{mailto:francismarfo9@gmail.com}{francismarfo9@gmail.com} | (402) 610-0555 | \href{https://www.linkedin.com/in/johndoe}{linkedin.com/in/francismarfo} |
\end{center}

% Education Section
\section*{EDUCATION}
\noindent
\textbf{University of Nebraska-Lincoln}, Lincoln, Nebraska \hfill Enrolled: August 2023 | Expected: July 2025\\ % University name and location
MSc. Statistics \hfill Overall GPA: N/A | Major GPA N/A\\ % Degree and GPA
Threads: Example and Example \hfill Credit standing: Honors % Additional info

% Experience Section
\section*{EXPERIENCE}
\noindent
\textbf{Social Security and National Insurance Trust} \hfill Dunkwa, Ghana\\ % Company name and location
\textit{Financial Data Officer} \hfill September 2021 - August 2022 % Position and duration
\begin{itemize}
    \item Validation of monthly contribution reports.
     \item Enrolement and re-enrolement of new members on the pension scheme.% Job responsibilities and achievements
\end{itemize}

% Additional Experience or Volunteer Work
\noindent
\textbf{Glokenneies Foundation} \hfill Accra, Ghana\\ % Project or organization name and location
\textit{Web developer \& publicity strategist, Volunteer} \hfill Month Year – Month Year % Position and duration
\begin{itemize}
    \item Developing and managing the website of Glokennies % Responsibilities and achievements
\end{itemize}

% Projects Section
\section*{PROJECTS}
\noindent
\textbf{Project Name} \hfill City, State\\ % Project name and location
\textit{Project Link:} \url{https://github.com/username/projectname} \hfill Month Year - Status % Project link and duration
\begin{itemize}
    \item Description of the project and your contributions. % Project description and contributions
\end{itemize}


% Skills Section
\section*{SKILLS}
\begin{itemize}
    \item \textbf{Relevant Coursework:} Calculus, Numerical Analysis, and Mathematical Statistic. % Relevant coursework
    \item \textbf{Programming:} Python, R, Visual Basic for Applications, and PHP. % Programming skills
    \item \textbf{Software:} SPSS. % Software skills
    \item \textbf{Communication:} Proficient in English language. % Communication skills
\end{itemize}

% End document
\end{document}
